---
title: "Complete Workflow for Bone Biomarker Review"
author: "Klaudia Adamowicz"
date: "2023-12-21"
output: 
  html_document:
    number_sections: false
    toc: true
    toc_float: true
    toc_depth: 5
---


# Setup

```{r setup, results='hide', message=FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE)
required_packages <- c("rmarkdown", "gprofiler2", "data.table", "ggplot2", "igraph", "reticulate", "plotly", "tidyr", "dplyr")
for(package in required_packages){
  if(!require(package,character.only = TRUE, quietly = TRUE)) install.packages(package, dependencies = TRUE, quietly = TRUE)
  library(package, character.only = TRUE, quietly = TRUE)
}

source("config.R")
source("functions/intersection_functions.R")
source("functions/network_enrichment_functions.R")
#source("functions/scoringFunctions.R")
#source("functions/IntersectionAnalysis.R")
#source("functions/graphAnalysis.R")

# set up environment
reticulate::virtualenv_create("bbr")
reticulate::py_install("drugstone", pip = TRUE, ignore_installed=TRUE, envname = "bbr")
reticulate::use_virtualenv("bbr")

# import python package
ds <- reticulate::import("drugstone")
ds$print_license()
ds$accept_license()

```

# Intersection Analysis

## Read Data (Gene Names)

Read protein list that has been processed with proharmed (filter ids, remap gene names, map to ensembl ids, map orthologs) for all studies except for the two ECM mouse studies (only map to ensembl ids, map orthologs) since they didn't reported proteins ids in their paper.

```{r}
# Read and preprocess the data
full_data <- as.data.frame(fread("data/cleaned_protein_list_uhh.csv", header = TRUE, na.strings = ""))
rownames(full_data) <- full_data$V1
full_data$V1 <- NULL

# Detect the first row where the first column is numeric, indicating data start
data_start_row <- which(sapply(rownames(full_data), function(x) grepl("^[0-9]+$", x)))[1]

# Save data information and subset the main data

data_info <- full_data[1:(data_start_row - 1),]
DT::datatable(data_info, options = list(scrollX = TRUE))

data <- full_data[data_start_row:nrow(full_data),]
DT::datatable(head(data), options = list(scrollX = TRUE))

# Explode data (one gene name per line, convert to numeric format)
data <- explode_data(data)
```

## Caclulate Weights and Intersections

```{r}
# Initialize a list to store intermediate data frames
intersections_list <- list()

for(tissue in names(tissue_list)) {
  if(weighting == "single") {
    intersections_list[[tissue]] <- get_intersection_dt(data = data, data_info = data_info, label = "Tissue", 
                                                        value = c(tissue_list[[tissue]]$label), 
                                                        assay = tissue_list[[tissue]]$assay, 
                                                        type = tissue)
  } else if(weighting == "double") {
    intersections_list[[tissue]] <- get_intersection_dt_double_weighting(data = data, data_info = data_info, label = "Tissue", 
                                                                        value = c(tissue_list[[tissue]]$label), 
                                                                        assay = tissue_list[[tissue]]$assay, 
                                                                        type = tissue)
  } else {
    stop("Exiting RMarkdown due to wrong/missing value for 'weighting' inside config.R.")
  }
}

# Combine all data frames into one
intersections <- do.call(rbind, intersections_list)
```

## Filter Intersectione

```{r}
# Group by 'Type' and apply select_intersections() function to each group
resulting_data_frames <- intersections %>%
  group_by(Type) %>%
  do(select_intersections(., intersection_thr=intersection_thr, weighting_thr=weighting_thr)) %>%
  ungroup()

# Combine resulting data frames into one
filtered_intersections <- bind_rows(resulting_data_frames)
```


## Save Intersections

```{r}
intersections_all <- intersections
intersections <- intersections[intersections$Intersected != 1,]
write.table(intersections_all, paste0(out_dir,"intersection_analysis_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
write.table(intersections, paste0(out_dir,"intersection_analysis_>1_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
write.table(filtered_intersections, paste0(out_dir, "filtered_intersection_analysis_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
DT::datatable(intersections)
```

## Visualizations

### Sizes of Datasets per Tissue

```{r}
# Assuming intersections_all is already defined and contains 'Gene' and 'Datasets' columns
intersections_all_exploded <- intersections_all %>%
  select(Gene, Datasets) %>%
  separate_rows(Datasets, sep = ";")

# Count occurrences of each unique element in "Datasets"
dataset_counts <- table(intersections_all_exploded$Datasets)

# Convert the counts to a dataframe
dataset_counts_df <- data.frame(Datasets = names(dataset_counts), Count = as.numeric(dataset_counts))
dataset_counts_df$Datasets <- factor(dataset_counts_df$Datasets, levels = names(data_info))
dataset_counts_df$Tissues <- unlist(c(data_info["Tissue", ])[dataset_counts_df$Datasets])
dataset_counts_df$Tissues <- dataset_counts_df$Tissues

# Create a mapping from original tissue names to new names using tissue_list
tissue_mapping <- unlist(lapply(names(tissue_list), function(tissue) setNames(rep(tissue, length(tissue_list[[tissue]]$label)), tissue_list[[tissue]]$label)))

# Replace tissue names using the mapping
dataset_counts_df$Tissues  <- sapply(dataset_counts_df$Tissues, function(x) tissue_mapping[[x]])
dataset_counts_df$Assay <- factor(sapply(dataset_counts_df$Tissues, function(x) tissue_list[[x]]$assay))
dataset_counts_df$Tissues <- factor(dataset_counts_df$Tissues)

# Create the boxplot with log-transformed y-axis
boxplot <- ggplot(dataset_counts_df, aes(x = Tissues, y = Count, fill = Tissues)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 2, alpha = 0.5) +  # Add jittered points
  scale_fill_manual(values = colors_for_levels) +  # Custom colors
  scale_y_log10() +  # Log-transform the y-axis
  facet_grid(. ~ Assay, scales = "free_x", space = "free_x") +  # Separate 'In vitro' and 'In vivo'
  labs(title = "Distribution of Dataset Counts by Tissue and Assay",
       x = "",
       y = "no. of DAPs per study (Log Scale)",
       fill = "Tissue") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        panel.spacing = unit(2, "lines"))  # Adjust spacing between panels

print(boxplot)
ggsave(paste0(out_dir, "dataset_sizes_per_tissue.png"), boxplot, width = 30, height = 15, units = "cm", dpi = 150, bg = "white")
```

### Sizes of Prior and Post WSI Filtering

```{r}
# Your existing pre-filtered data preparation
genes_per_tissue <- intersections_all %>%
  rename(Tissue = Type) %>%
  group_by(Tissue) %>%
  summarise(SumUniqueGenes = n_distinct(Gene)) %>%
  mutate(DataType = "Pre-Filtered")

# Prepare post-filtered data
filtered_genes_per_tissue <- filtered_intersections %>%
  rename(Tissue = Type) %>%
  group_by(Tissue) %>%
  summarise(SumUniqueGenes = n_distinct(Gene)) %>%
  mutate(DataType = "Post-Filtered")

# Combine both datasets
combined_genes_data <- rbind(genes_per_tissue, filtered_genes_per_tissue)

combined_genes_data$DataType <- factor(combined_genes_data$DataType, levels = c("Pre-Filtered", "Post-Filtered"))

# Create the bar plot
bar_plot <- ggplot(combined_genes_data, aes(x = Tissue, y = SumUniqueGenes, fill = Tissue, alpha = DataType)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_text(aes(label = SumUniqueGenes), 
            position = position_dodge(width = 0.8), vjust = -0.5, size = 3) +
  scale_y_log10() + # Log-transform the y-axis
  scale_fill_manual(values = colors_for_levels) +
  scale_alpha_manual(values = c(1, 0.5)) + # Pre-filtered bars are 50% transparent
  labs(title = "Sum of Unique Genes Per Tissue (Pre and Post Filtering)",
       x = "",
       y = "Sum of Unique Genes") +
  theme_minimal() +
  theme(axis.text.x = element_blank()) # Rotate x-axis labels for readability

print(bar_plot)
ggsave(paste0(out_dir, "sizes_per_tissue_pre_and_post_filtering.png"), bar_plot, width = 30, height = 15, units = "cm", dpi = 150, bg = "white")
```

### Filtering based on Intersection and Weight

```{r}
# For reproducibility, set a seed
set.seed(123)

# Loop over each unique value in the 'Type' column
for (type in unique(intersections_all$Type)) {
  
  # Subset the dataframe
  subset_df <- intersections_all[intersections_all$Type == type, ]
  filtered_subset_df <- filtered_intersections[filtered_intersections$Type == type, ]
  
  # Call your custom function
  result <- plot_weighted_intersection(weighted_dt=subset_df,
                                        min_intersected=floor(filtered_subset_df$Size[[1]]/intersection_thr), 
                                        min_weight=min(filtered_subset_df$Weight))
  
  # Save the plot
  ggsave(paste0(out_dir, "barchart_plot_", type, ".png"), plot = result[[1]], device = "png", width = 10, height = 8, units = "in")
  
  # Save the dataframe
  write.csv(result[[2]], file = paste0(out_dir, "barchart_data_", type, ".csv"), row.names = FALSE)
}
```

## Identify Core Genes

```{r}
# Check for duplicated genes across different Types
duplicated_genes <- filtered_intersections %>%
  group_by(Gene) %>%
  summarize(unique_types = n_distinct(Type), types = paste(Type, collapse = "; ")) %>%
  filter(unique_types > 1) %>%
  arrange(desc(unique_types))

write.table(duplicated_genes, paste0(out_dir,"core_analysis_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
# Display duplicated genes and their unique Type counts
DT::datatable(duplicated_genes)
```

# Network Enrichment

## Generate Networks

### Core Genes

```{r}
seeds <- unique(duplicated_genes$Gene)
core_ami_ds <- run_drugstone_ami(seeds)
core_drugs_ds <- run_drugstone_drugs(core_ami_ds$ds_genes, core_ami_ds$ds_edges)
save_results(core_drugs_ds, "core_genes")
```

### Tissue Genes

```{r}
de_results_types <- list("ami" = list(), "drugs" = list())
for (type in unique(filtered_intersections$Type)) {
  print(type)
  subset <- subset(filtered_intersections, Type == type)
  de_results_types[["ami"]][[type]] <- run_drugstone_ami(subset$Gene)
  de_results_types[["drugs"]][[type]] <- run_drugstone_drugs(de_results_types[["ami"]][[type]]$ds_genes,
                                                             de_results_types[["ami"]][[type]]$ds_edges)
  save_results(ds_result = de_results_types[["drugs"]][[type]], filename = paste0(type))
}
```

