---
title: "Complete Workflow for Bone Biomarker Review"
author: "Klaudia Adamowicz"
date: "2023-12-21"
output: 
  html_document:
    number_sections: false
    toc: true
    toc_float: true
    toc_depth: 5
---


# Setup

```{r setup, results='hide', message=FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE)
required_packages <- c("rmarkdown", "gprofiler2", "data.table", "ggplot2", "igraph", "reticulate", "plotly", "tidyr", "dplyr", "GGally", "ComplexHeatmap", "circlize", "readxl", "ggpattern", "stringr", "openxlsx", "ggtext", "ggpubr", "scatterpie")
for(package in required_packages){
  if(!require(package,character.only = TRUE, quietly = TRUE)) install.packages(package, dependencies = TRUE, quietly = TRUE)
  library(package, character.only = TRUE, quietly = TRUE)
}

remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)


source("config.R")
sapply(list.files("functions/", pattern = ".R", full.names = TRUE), source)

# set up environment
reticulate::virtualenv_create("bbr")
reticulate::py_install("drugstone", pip = TRUE, ignore_installed=TRUE, envname = "bbr")
reticulate::use_virtualenv("bbr")

# import python package
ds <- reticulate::import("drugstone")
ds$print_license()
ds$accept_license()
```

# Read Data

```{r}
# Read original meta-study data on gene name level
original_data_genes <- read_meta_study_data(file_path = original_study_file, "Gene names")
data_info <- original_data_genes$`meta-info`
original_data_genes <- original_data_genes$data

# Read original meta-study data on protein level
original_data_proteins <- read_meta_study_data(file_path = original_study_file, "UniprotAC")
original_data_proteins <- original_data_proteins$data

# Explode original data
original_data_genes_exploded <- explode_data(original_data_genes)
original_data_proteins_exploded <- explode_data(original_data_proteins)
```

# Harmonization of Data

```{r}
harm_out_dir <- paste0(out_dir, "harmonization/")
dir.create(file.path(harm_out_dir), showWarnings = FALSE)
```

```{r}
# TODO: harmonization function -> check if study 27 is mouse
harmonized_data <- run_proharmed(gene_level = original_data_genes, protein_level = original_data_proteins)

# Save harmonized data
#TODO

# Read harmonized data from paper:
harmonized_data <- readRDS(paste0(harm_out_dir, "harmonized_data.rds"))

# Explode harmonized data
data <- explode_data(harmonized_data)
```

## Visualizations

### Venn Diagrams

```{r}
harmonization_venns <- create_harmonization_venn_diagrams(data_info)
harmonization_venns
ggsave(paste0(harm_out_dir, "pie_plots_studies.png"), width = 12, height = 4.5)
```

### Harmonization Logging Figure 

```{r}
plot_proharmed_logging("data/results/harmonization/logging/")
ggsave(paste0(harm_out_dir, "proharmed_logging.png"), width = 8, height = 12)

```
# Intersection Analysis of Tissue-Specific Proteins

```{r}
in_out_dir <- paste0(out_dir, "intersection/")
dir.create(file.path(in_out_dir), showWarnings = FALSE)
```

## Calculate Weights and Intersections for each Tissue

```{r}
# Intersections of Harmonized Data
intersections <- calculate_intersections(data, data_info, tissue_list, weighting)

# Intersections of Original Data
intersections_original <- calculate_intersections(original_data_genes_exploded, data_info, tissue_list, weighting)
# remove 9_human -> no gene names provided intersection
intersections_original <- intersections_original[intersections_original$Gene != "no Gene names provided",]

```

## Filter Intersections

```{r}
# Intersections of Harmonized Data
filtered_intersections <- filter_intersections(intersections, intersection_thr, weighting_thr)

# Intersections of Original Data
filtered_intersections_original <- filter_intersections(intersections_original, intersection_thr, weighting_thr)
```

## Save Intersections

```{r}
# Only save harmonized intersections
intersections_all <- intersections

intersections <- intersections[intersections$Intersected != 1,]

filtered_intersections <- filtered_intersections[filtered_intersections$Intersected != 1,]

write.table(intersections_all, paste0(in_out_dir,"intersection_analysis_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
write.table(intersections, paste0(in_out_dir,"intersection_analysis_>1_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
write.table(filtered_intersections, paste0(in_out_dir, "filtered_intersection_analysis_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
DT::datatable(intersections)
```

## Visualizations

### Summary of included studies and selection of co-affected proteins

```{r}

# Sankey on the number of studies per tissue and species 
sankey <- generate_sankey_plot(data_info, colors_for_levels)

# Number of extracted DAPs per study and tissue type
boxplot_DAPs <- plot_boxplot_DAPS(intersections_all, data_info, tissue_list, colors_for_levels)

# Number of CAPs per study and tissue type (pre-filtered and post-filtered)
barplot_CAPs <- plot_barplot_CAPS(intersections_all, filtered_intersections, tissue_list, colors_for_levels)

# Combine for paper figure 3
p <- ggarrange(boxplot_DAPs, barplot_CAPs, ncol = 2, labels = c("B", "C"), font.label = list(size = 16), legend = "none")
ggarrange(sankey, p, ncol = 2, labels = c("A", ""), heights = c(0.7, 1), font.label = list(size = 16), legend.grob = get_legend(barplot_CAPs), legend = "bottom")
ggsave(paste(in_out_dir, "overview_plots.png"), width = 8, height = 3)
```

### WSI for each tissue

```{r}
# For reproducibility, set a seed
set.seed(123)
plots <- list()
# Loop over each unique value in the 'Type' column
for (type in unique(intersections_all$Type)) {
  
  # Subset the dataframe
  subset_df <- intersections_all[intersections_all$Type == type, ]
  filtered_subset_df <- filtered_intersections[filtered_intersections$Type == type, ]
  
  # Call your custom function
  result <- plot_weighted_intersection(weighted_dt=subset_df,
                                        min_intersected=floor(filtered_subset_df$Size[[1]]/intersection_thr), 
                                        min_weight=min(filtered_subset_df$Weight))
  
  # Plots
  plots[[type]] <- result[[1]] + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + labs(x = "Intersections")
}

p1 <- ggarrange(plots$Cells, plots$EVs, common.legend = TRUE, ncol = 1, labels = c("A","B"), legend = "none")
p2 <- ggarrange(plots$ECM, plots$Bone, plots$`Liquid-Biopsy`, nrow = 1, labels = c("C", "D", "E"), legend = "none")
ggarrange(p1, p2, ncol = 1, labels = NULL, common.legend = FALSE, legend = "bottom", heights = c(2,1), legend.grob = get_legend(plots$Cells))
ggsave(paste0(in_out_dir, "weighted_intersections_all.png"), width = 10, height = 12)
```

### Intersection Size in Harmonized Data and Original Data

```{r}
plot_original_vs_harmonized_intersections(intersections_all, filtered_intersections, intersections_original) # TODO: bug fixing -> figure not the same as previously
ggsave(paste0(in_out_dir, "pieplot_original_vs_harmonization.png"), width = 10, height = 12)

```

# Identification of Core Genes

```{r}
# Check for duplicated genes across different Types
duplicated_genes <- filtered_intersections %>%
  group_by(Gene) %>%
  summarize(unique_types = n_distinct(Type), types = paste(Type, collapse = "; ")) %>%
  filter(unique_types > 1) %>%
  arrange(desc(unique_types))

write.table(duplicated_genes, paste0(in_out_dir,"core_analysis_df.csv"), quote=FALSE, sep="\t", row.names = FALSE)
# Display duplicated genes and their unique Type counts
DT::datatable(duplicated_genes)
```


TODO: Kikki -> ab hier nochmal kucken. Network enrichment code hab ich auch nicht so wirklich gefunden

# Network Enrichment

```{r}
ne_out_dir <- paste0(out_dir, "netenrich/")
dir.create(file.path(ne_out_dir), showWarnings = FALSE)
```

## Generate Networks

### Comparative Analysis of BioGRID, IID, NeDRex, and STRING

TODO: add two supplementary plots

### Core Genes

```{r}
seeds <- unique(duplicated_genes$Gene)
core_ami_ds <- run_drugstone_ami(seeds)
core_drugs_ds <- run_drugstone_drugs(core_ami_ds$ds_genes, core_ami_ds$ds_edges)
save_results(core_drugs_ds, "core_genes", ne_out_dir)
```

### Tissue Genes

```{r}
de_results_types <- list("ami" = list(), "drugs" = list())
for (type in unique(filtered_intersections$Type)) {
  print(type)
  subset <- subset(filtered_intersections, Type == type)
  de_results_types[["ami"]][[type]] <- run_drugstone_ami(subset$Gene)
  de_results_types[["drugs"]][[type]] <- run_drugstone_drugs(de_results_types[["ami"]][[type]]$ds_genes,
                                                             de_results_types[["ami"]][[type]]$ds_edges)
  save_results(ds_result = de_results_types[["drugs"]][[type]], filename = paste0(type), ne_out_dir)
}
```

## Visualizations

```{r}
ne_vis_out_dir <- paste0(ne_out_dir, "visualizations/")
dir.create(file.path(ne_vis_out_dir), showWarnings = FALSE)
```

```{r}
# Plotting the graph
color_palette <- c("seed" = "lightblue", "new" = "red", "significant only in single tissue" = "lightgreen", 
                   "filtered out for single tissue" = "orange", "drug" = "violet")
```

### Tissue Networks

TODO: check if we need all this (drugs code could be removed no?)

```{r}
networks_tissues <- list()

# Loop over each type
for (type in unique(filtered_intersections$Type)) {
  set.seed(123)

  subset <- subset(filtered_intersections, Type == type)

  # Extract gene categories for each type
  gene_categories <- extract_gene_categories(
    seeds = subset$Gene,
    ds_results = de_results_types[["drugs"]][[type]],
    filtered_intersections = filtered_intersections,
    all_genes = rownames(data)
  )

  # Prepare node attributes for the graph without drugs
  node_info_without_drugs <- prepare_node_attributes(
    graph = de_results_types[["ami"]][[type]]$ds_graph,
    gene_categories = gene_categories
  )
  
   # Change names
  node_info_without_drugs$attributes[node_info_without_drugs$attributes == "filtered out for single tissue"] <- "filtered out after WSI"
  node_info_without_drugs$attributes[node_info_without_drugs$attributes == "significant only in single tissue"] <- "significant in other tissues"

  # Update graph with node attributes and types for the graph without drugs
  de_results_types[["ami"]][[type]]$ds_graph <- igraph::set_vertex_attr(de_results_types[["ami"]][[type]]$ds_graph, "node_attributes", value = node_info_without_drugs$attributes)
  de_results_types[["ami"]][[type]]$ds_graph <- igraph::set_vertex_attr(de_results_types[["ami"]][[type]]$ds_graph, "node_type", value = node_info_without_drugs$types)

  # Plot the graph without drugs
  p_without_drugs <- ggnet2(de_results_types[["ami"]][[type]]$ds_graph, size = "degree", color = "node_attributes", shape = "node_type", 
              color.palette = color_palette_new, label = TRUE, label.size = 2, edge.alpha = 0.75, node.alpha = 0.85) + guides(size = FALSE) + 
  scale_color_manual(name = "Node Attributes", values = color_palette_new) +
  scale_shape_manual(values = c("circle", "triangle"), labels = c("seed", "exception"), name = "Node Type")
  networks_tissues[[type]] <- p_without_drugs
}
```

Save networks in the correct format to manuscript

```{r}
# Cells
ggsave(paste0(ne_vis_out_dir, "Cells-ami_graph.png"), networks_tissues$Cells, width = 10, height = 7, dpi = 300)
# EVs
ggsave(paste0(ne_vis_out_dir, "EVs-ami_graph.png"), networks_tissues$EVs, width = 10, height = 7, dpi = 300)
# ECM
ggsave(paste0(ne_vis_out_dir, "ECM-ami_graph.png"), networks_tissues$ECM, width = 10, height = 7, dpi = 300)
# Bone
ggsave(paste0(ne_vis_out_dir, "Bone-ami_graph.png"), networks_tissues$Bone, width = 10, height = 7, dpi = 300)
# Liquid-Biopsy
ggsave(paste0(ne_vis_out_dir, "Liquid-Biopsy-ami_graph.png"), networks_tissues$`Liquid-Biopsy`, width = 10, height = 7, dpi = 300)
```

Extract network sizes as table for manuscript

```{r}
# extract table of network sizes
network_sizes <- sapply(names(networks_tissues), function(x){
  tmp <- table(networks_tissues[[x]]$data$color) %>% as.matrix() %>% t() %>% as.data.frame()
  rownames(tmp) <- x
  return(tmp)
})

network_sizes <- rbindlist(network_sizes, fill = TRUE, idcol = TRUE)
colnames(network_sizes)[1] <- "Tissue"
network_sizes <- network_sizes[, c("Tissue", "seed", "new", "filtered out after WSI", "significant in other tissues")]

# save network data as excel sheet
networks_tissues_data <- lapply(networks_tissues, function(x){
  dt <- x$data[, c("label", "color", "shape")]
  colnames(dt) <- c("Gene", "Node Type", "Node Attributes")
  return(dt)
})

networks_tissues_data[["Core Network"]] <- core_network_data
openxlsx::write.xlsx(networks_tissues_data, file = paste(ne_vis_out_dir, "network_tissues_data.xlsx"))
```

### Core Network

```{r}
set.seed(123)

gene_categories <- extract_gene_categories(seeds = duplicated_genes$Gene, 
                                           ds_results = core_ami_ds, 
                                           filtered_intersections = filtered_intersections, 
                                           all_genes = rownames(data))

# Using the updated function
node_info <- prepare_node_attributes(graph = core_ami_ds$ds_graph, gene_categories = gene_categories)
core_ami_ds$ds_graph <- igraph::set_vertex_attr(core_ami_ds$ds_graph, "node_attributes", value = node_info$attributes)
core_ami_ds$ds_graph <- igraph::set_vertex_attr(core_ami_ds$ds_graph, "node_type", value = node_info$types)

p <- ggnet2(core_ami_ds$ds_graph, size="degree", color = "node_attributes", shape = "node_type", 
            color.palette =  color_palette, label=TRUE, label.size = 3) + guides(size = FALSE) + 
   scale_color_manual(name = "Node Attributes", values = color_palette) +
  scale_shape_manual(values = c("circle", "triangle"), labels = c("seed", "exception"), name = "Node Type")

# save network data as excel sheet
core_network_data <- p$data[, c("label", "color", "shape")]
colnames(core_network_data) <- c("Gene", "Node Type", "Node Attributes")

ggsave(paste0(ne_vis_out_dir, "core_genes_graph.png"), p, width = 10, height = 7, dpi = 300)
print(p)
```

# Tissue Networks - Functional Enrichment

TODO: network enrichment -> wo hast du das gemacht?

TODO: heatmap of network enrichment -> currently still in old script: Johannes_Heatmap.R script


# Core Network - Scorings

## Network Scorings

```{r}
network_scoring <- score_gene_network(g = core_ami_ds$ds_graph, attribute_name = "name")
network_scoring <- network_scoring[, c("IDs", colnames(network_scoring)[colnames(network_scoring) != "IDs"]), with = FALSE]
```

## Enrichement Scorings

```{r}
enrich_scoring <- score_genes_enrichment(genes = core_ami_ds$ds_genes)
```

## Accessibility Scorings

```{r}
access_scoring <- read_excel("data/input/Accessibility_BoneAbundance_Scores.xlsx", sheet = "accessibility")
access_scoring[access_scoring$IDs == "TGM2", "IDs"] <- "HEL-S-45"
```

## Bone Abundance Scorings

```{r}
boneabund_scoring <- read_excel("data/input/Accessibility_BoneAbundance_Scores.xlsx", sheet = "bone abundance")
boneabund_scoring[boneabund_scoring$IDs == "TGM2", "IDs"] <- "HEL-S-45"
```

## Digest Results

```{r}
digest_results <- read.csv("data/input/core_sc_results.csv")
colnames(digest_results)[1] <- "IDs"
digest_long <- melt(data.table(digest_results), id.vars = "IDs", variable.name = "type", value.name = "score")
digest_medians <- digest_long %>% group_by(IDs) %>% summarise(median_score = median(score)) %>% as.data.table()
colnames(digest_medians)[2] <- "DIGEST"
```

## Literature Results

```{r}
literature_results <- read_excel("data/input/literature_versand.xlsx", sheet = "Tabelle1") # check if current version with SERPINA1 = beneficial
literature_results <- as.data.table(literature_results)
colnames(literature_results)[2] <- "Literature"
```

## Drugs

```{r}
drugs <- get_top_drugs(genes = core_ami_ds$ds_genes, number = 1000L)
drug_scores <- calculate_drug_connections(drugs, network_scoring$IDs)
```

## Final Overview Heatmap of Scores

Generate combined data frame of all ranks:

```{r}
all_ranks <- generate_combined_ranking_dt(network_scoring, enrich_scoring, access_scoring, boneabund_scoring)

# Save order of IDs
ids_order <- all_ranks$IDs

# Process data to correct format
row.names(all_ranks) <- all_ranks$IDs
all_ranks$IDs <- NULL
colnames(all_ranks) <- c("Enrichment Rank", "Network Rank", "Accessibility Rank", "Bone Abundance Rank")

# Color Scale for Ranks
col_fun <- colorRamp2(c(1,10, max(all_ranks)), c("#4BA999", "#FFC107", "white"))
nr <- nrow(all_ranks)
```

Generate annotations for heatmap:

```{r}
# tissue and assay annotation
att_df <- as.data.frame(get.vertex.attribute(combined_nodrug_graph))
att_df_core <- att_df[att_df$name %in% V(core_ami_ds$ds_graph)$name,]
tissue_annotation <- att_df_core$source
names(tissue_annotation) <- att_df_core$name

tmp <- generate_tissue_assay_file_anno_vec(tissue_annotation, tissue_list, ids_order, colors_for_levels, out_dir)
tissue_anno_vec <- tmp$tissue
assay_anno_vec <- tmp$assay

# type annotation (seed, new, filtered out for single tissue)
type_annotation <- igraph::as_data_frame(core_drugs_ds$ds_graph, what= "vertices")["node_attributes"]
type_annotation <- type_annotation[match(ids_order, rownames(type_annotation)),]
names(type_annotation) <- ids_order

# drug annotation
drug_annotation <- drug_scores[match(ids_order, drug_scores$IDs), "drugs"]
drug_colors <- colorRamp2(c(0, max(drug_annotation)), c("white", "red"))

# digest annotation
digest_medians <- digest_medians[match(ids_order, digest_medians$IDs),]
col_fun_digest <- colorRamp2(c(-max(abs(digest_medians$DIGEST)),0,max(abs(digest_medians$DIGEST))), c("dodgerblue3", "white", "firebrick"))

# literature annotation
literature_results <- literature_results[match(ids_order, literature_results$IDs),]
literature_colors <- c("grey70","#CC0066","#4DAF4A","#984EA3")
names(literature_colors) <- unique(literature_results$Literature)

# generate one ComplexHeatmap rowAnnotation of all single annotations
right_annotation <- rowAnnotation(DIGEST = anno_simple(digest_medians$DIGEST, col = col_fun_digest, gp = gpar(col = "black")),
                                  Drugs = anno_simple(drug_annotation, pch =  paste(drug_annotation), col = drug_colors, pt_size = unit(0.4, "cm"), gp = gpar(col = "black")),
                                  Literature = literature_results$Literature,
                                  Type = type_annotation, 
                                  Tissue = anno_image(tissue_anno_vec, which = "row", border = TRUE, 
                                                      gp = gpar(col = "black"), space = unit(0, "cm")),
                                  Assay = anno_image(assay_anno_vec, which = "row", border = TRUE,
                                                     gp = gpar(col = "black"), space = unit(0, "cm")),
                                  col = list(Type = color_palette[unique(type_annotation)], Literature = literature_colors), 
                                  gp = gpar(col = "black"),
                                  show_legend = FALSE,
                                  gap = unit(0.2, "cm"))
```

Plot heatmap:

```{r}
scoring_heatmap <- Heatmap(as.matrix(all_ranks),
  name = "measure",
  col = col_fun,
  show_row_names = TRUE,
  border = TRUE,
  border_gp = gpar(col = "black"),
  rect_gp = gpar(col = "black"),
  show_column_names = TRUE,
  cluster_rows = TRUE,
  cluster_columns = FALSE,
  right_annotation = right_annotation,
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.text(all_ranks[i, j], x, y, gp = gpar(fontsize = 10)) # Adjust fontsize as needed
  },
  show_heatmap_legend = FALSE,
  height = unit(0.5, "cm")*nr,
  width = unit(6, "cm")
)

ht_opt$ROW_ANNO_PADDING <- unit(0.1, "cm")
```

Generate legends:

```{r}
tissue_legend <- Legend(labels = names(tissue_list), title = "Tissue", legend_gp = gpar(fill = colors_for_levels[names(tissue_list)], type = "grid"))
assays <- c("In vitro", "In vivo")
assay_legend <- Legend(labels = assays, title = "Assay", legend_gp = gpar(fill = colors_for_levels[assays], type = "grid"))
heatmap_legend <- Legend( title = "Measure Rank",
    at = c(1, 10, max(all_ranks)),
    labels = c("1 (Best)", "10", paste0(max(all_ranks)," (Worse)")), col_fun = col_fun)
type_legend <- Legend(labels = unique(type_annotation), title = "Type", legend_gp = gpar(fill = color_palette[unique(type_annotation)], type = "grid"))
drug_legend <- Legend(col_fun = drug_colors, title = "Drugs", at = c(0, max(drug_annotation)))
digest_legend <- Legend(title =  "Significance Contribution (DIGEST)",
                        col_fun = col_fun_digest)
literature_legend <- Legend(labels = unique(literature_results$Literature), title = "Literature", legend_gp = gpar(fill = literature_colors), type = "grid")
```

Save heatmap: 

```{r}
tiff(paste0(out_dir, "scoring/scoring_heatmap.tiff"), width=12,height=13,units="in",res=1200)
draw(scoring_heatmap, annotation_legend_list = list(heatmap_legend, digest_legend, drug_legend, literature_legend, type_legend, tissue_legend, assay_legend), annotation_legend_side = "right", ht_gap = unit(0.5, "cm"), auto_adjust = TRUE)
dev.off()
```

Generate excel sheet with scoring information: 

```{r}
# save scores
all_ranks$IDs <- row.names(all_ranks)

# order digest results by ID
digest_results <- digest_results[match(enrich_scoring$IDs, digest_results$IDs),]

# digest medians
final_ranks <- merge(all_ranks, digest_medians, by = "IDs")
#drugs
tmp_drugs <- drug_scores[, c("IDs", "drugs")]
colnames(tmp_drugs) <- c("IDs", "Drugs")
final_ranks <- merge(final_ranks, tmp_drugs, by = "IDs")
#tissue
tissue_dt <- data.frame(IDs = names(tissue_annotation), Tissue = tissue_annotation)
final_ranks <- merge(final_ranks, tissue_dt, by = "IDs", all.x = TRUE)
#type
type_dt <- data.frame(IDs = names(type_annotation), Type = type_annotation)
final_ranks <- merge(final_ranks, type_dt, by = "IDs")
#literature

final_ranks <- merge(final_ranks, literature_results, by = "IDs")
# order as in heatmap

# reorder network scoring
network_scoring <- network_scoring[match(enrich_scoring$IDs, network_scoring$IDs),]
network_scoring <- network_scoring[, c(6, 1, 2, 3, 4, 5, 7, 8, 9, 10, 11)]

data_names <- list(
  "Overview" = final_ranks,
  "Network Scores + Ranks" = network_scoring,
  "Enrichment Scores + Ranks" = enrich_scoring,
  "Accessibility Scores + Ranks" = access_scoring,
  "Bone Abundance Scores + Ranks" = boneabund_scoring,
  "DIGEST" = digest_results,
  "Drugs" = drugs
)
openxlsx::write.xlsx(data_names, file = paste(out_dir, "scoring/scoring_heatmap_data.xlsx"))
```

# What is with this?

## Enrichment Term Analysis

```{r}
prop <- fread("../BoneBiomarkerReview/data/results/go_networks/term_intersections_proportions.tsv")
prop1 <- prop[prop$term_name == "cell adhesion",]

seeds <- strsplit(prop1$intersecting_genes_all[1], ", ")[[1]]
ami_ds <- run_drugstone_ami(seeds)
drugs_ds <- run_drugstone_drugs(ami_ds$ds_genes, ami_ds$ds_edges)
```

```{r}
# Select only the columns 'intersecting_genes' and 'dataframes'
selected_data <- prop1[, .(intersecting_genes, dataframes)]

# Split 'intersecting_genes' by ", " and explode the rows
exploded_data <- selected_data[, strsplit(intersecting_genes, ", "), by = .(dataframes)]

# Convert the list column to individual rows
exploded_data_long <- exploded_data[, .(intersecting_gene = unlist(V1)), by = .(dataframes)]
exploded_data_long[, dataframes := gsub(", ", ";", dataframes)]

list_by_gene <- split(exploded_data_long$dataframes, exploded_data_long$intersecting_gene)
```

```{r}
seed_att <- sapply(igraph::get.vertex.attribute(drugs_ds$ds_graph)$name, function(x) {ifelse(x %in% seeds,  list_by_gene[[x]],  ifelse(x %in% names(drugs_ds$ds_drugs),  "drug",  "exception"))})
drugs_ds$ds_graph <- igraph::set_vertex_attr(drugs_ds$ds_graph, "node_source", value = seed_att)
```


```{r}
colors_for_levels <- c(
  "EVs" = "#A3A500",
  "Cells" = "#F8766D",
  "Liquid-Biopsy" = "#E76BF3",
  "Bone" = "#00B0F6",
  "ECM" = "#00BF7D",
  "exception" = "lightgrey",
  "drug" = "#7C7C7C"
)
png(file=paste0("cell_adhesion_metwork_with_drugs.png"), height = 2000, width = 3000, res=100)
draw_pie_chart_network(graph = drugs_ds$ds_graph, 
                       attributes = as.data.frame(get.vertex.attribute(drugs_ds$ds_graph)), 
                       all_pie_values = names(colors_for_levels),
                       pie_column = "node_source",
                       pie_colors = colors_for_levels,
                       label = TRUE,
                       seed = 123,
                       legend_position = "topleft")
dev.off()
```

```{r}
seed_att <- sapply(igraph::get.vertex.attribute(ami_ds$ds_graph)$name, function(x) {ifelse(x %in% seeds,  list_by_gene[[x]], "Exception")})
ami_ds$ds_graph <- igraph::set_vertex_attr(ami_ds$ds_graph, "node_source", value = seed_att)

colors_for_levels <- c(
  "EVs" = "#A3A500",
  "Cells" = "#F8766D",
  "Liquid-Biopsy" = "#E76BF3",
  "Bone" = "#00B0F6",
  "ECM" = "#00BF7D",
  "Exception" = "lightgrey"
)
png(file=paste0("cell_adhesion_metwork.png"), height = 2000, width = 3000, res=100)
draw_pie_chart_network(graph = ami_ds$ds_graph, 
                       attributes = as.data.frame(get.vertex.attribute(ami_ds$ds_graph)), 
                       all_pie_values = names(colors_for_levels),
                       pie_column = "node_source",
                       pie_colors = colors_for_levels,
                       label = TRUE,
                       seed = 123,
                       legend_position = "topleft")
dev.off()
```

```{r}
save_results(drugs_ds, "cell_adhesion_genes", "")
```


```{r}
prop2 <- prop[prop$term_name == "collagen-containing extracellular matrix",]

seeds <- strsplit(prop2$intersecting_genes_all[1], ", ")[[1]]
ami_ds <- run_drugstone_ami(seeds)
drugs_ds <- run_drugstone_drugs(ami_ds$ds_genes, ami_ds$ds_edges)
```

```{r}
# Select only the columns 'intersecting_genes' and 'dataframes'
selected_data <- prop2[, .(intersecting_genes, dataframes)]

# Split 'intersecting_genes' by ", " and explode the rows
exploded_data <- selected_data[, strsplit(intersecting_genes, ", "), by = .(dataframes)]

# Convert the list column to individual rows
exploded_data_long <- exploded_data[, .(intersecting_gene = unlist(V1)), by = .(dataframes)]
exploded_data_long[, dataframes := gsub(", ", ";", dataframes)]

list_by_gene <- split(exploded_data_long$dataframes, exploded_data_long$intersecting_gene)
```

```{r}
seed_att <- sapply(igraph::get.vertex.attribute(drugs_ds$ds_graph)$name, function(x) {ifelse(x %in% seeds,  list_by_gene[[x]],  ifelse(x %in% names(drugs_ds$ds_drugs),  "drug",  "exception"))})
drugs_ds$ds_graph <- igraph::set_vertex_attr(drugs_ds$ds_graph, "node_source", value = seed_att)
```


```{r}
colors_for_levels <- c(
  "EVs" = "#A3A500",
  "Cells" = "#F8766D",
  "Liquid-Biopsy" = "#E76BF3",
  "Bone" = "#00B0F6",
  "ECM" = "#00BF7D",
  "exception" = "lightgrey",
  "drug" = "#7C7C7C"
)
png(file=paste0("collagen-containing_EM_metwork_with_drugs.png"), height = 2000, width = 3000, res=100)
draw_pie_chart_network(graph = drugs_ds$ds_graph, 
                       attributes = as.data.frame(get.vertex.attribute(drugs_ds$ds_graph)), 
                       all_pie_values = names(colors_for_levels),
                       pie_column = "node_source",
                       pie_colors = colors_for_levels,
                       label = TRUE,
                       seed = 123,
                       legend_position = "topleft")
dev.off()
```

```{r}
seed_att <- sapply(igraph::get.vertex.attribute(ami_ds$ds_graph)$name, function(x) {ifelse(x %in% seeds,  list_by_gene[[x]], "Exception")})
ami_ds$ds_graph <- igraph::set_vertex_attr(ami_ds$ds_graph, "node_source", value = seed_att)

colors_for_levels <- c(
  "EVs" = "#A3A500",
  "Cells" = "#F8766D",
  "Liquid-Biopsy" = "#E76BF3",
  "Bone" = "#00B0F6",
  "ECM" = "#00BF7D",
  "Exception" = "lightgrey"
)
png(file=paste0("collagen-containing_EM_metwork.png"), height = 2000, width = 3000, res=100)
draw_pie_chart_network(graph = ami_ds$ds_graph, 
                       attributes = as.data.frame(get.vertex.attribute(ami_ds$ds_graph)), 
                       all_pie_values = names(colors_for_levels),
                       pie_column = "node_source",
                       pie_colors = colors_for_levels,
                       label = TRUE,
                       seed = 123,
                       legend_position = "topleft")
dev.off()
```

```{r}
save_results(drugs_ds, "collagen-containing_EM", "")
```
```

